STA610 Case Study 1 Team 4 Report

### 2021-03-20 STA 610 Case Study 1 Report_Team 4.Rmd
Added pacman to handle dependencies

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(lme4)
library(gridExtra)
library(grid)
library(ggplot2)
library(lattice)
#devtools::install_github("goodekat/redres")
library(redres)
```

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(tidyverse, lme4, gridExtra, grid, ggplot2, lattice, redres)
#devtools::install_github("goodekat/redres")
```
